\section{Cloud Architecture}

In this section, the \ac{EO} architecture on cloud is fully described. As
mentioned, the cloud infrastructure where this system is implemented is provided
by \bonfire multi-cloud. The \emph{Orchestrator}, \emph{Archive and Catalogue} and \emph{Processing
Chain} integrate the cloud components for processing, archiving and cataloging
Earth's surface images. This modules are summarized as follows:
\begin{itemize}
\item \emph{Orchestrator:} it manages the automatic distribution of the raw data to the processors. It handles the complete automatic processing chain execution.  If the processor chain is occupied, the manager replicates the complete chain in a new machine.
\item \emph{Processing Chain:} it processes the raw data and converts it in orthorectified images. 
\item \emph{Archive and catalogue:} it is the place where the processed images are stored and catalogued for its distribution.
\end{itemize}


There are two implementations of this architecute: the first one uses \ac{SSH}
and \ac{SCP} for communications and the processing is limited to one chain
processing each time; the second one is based in the distributed middleware
ZeroC ICE and it takes advantage of the use of the location transparency, server
replication and replication service in order to satisfy all request for
processing images. This implementation only is a prototype. It is not fully
complete because there were some troubles with its implementation in \bonfire
owing to the network policies imposed by the platform. 


In the following sections, these cloud architectures are detailed. Firstly, the
componets which appear in both architecture such as Orchestrator,
ProcessingChain and Archive and Catalogue modules are explained. Then, both
architectures and its components are hardly studied. In each architecture
description, the architecture design is elaborated and then, the communications
between the components, the implementation, its executions and its
implementations in \bonfire are shown.

%% First, the product
%% processors compose the \emph{Processing Chain} are shown. These processors are owned
%% by Elecnor Deimos company, so they are not fully described but the main features
%% are exposed. Then, the \emph{Archive and Catalogue}
%% module is described. Finally, the \emph{Orchestrator} component that manages all the
%% cloud processes is fully explained and detailed.


\input{platform-on-cloud.tex}

