
\chapter{The Geo-Cloud Experiment}
\label{chap:geocloud-experiment}
\drop{T}{he} GEO-Cloud experiment consists of the emulation of a realistic and complete Earth Observation System that provides services using cloud technology. For that purpose a constellation of satellites, ground stations, a cloud architecture, use cases and end users' models were designed.

The \ac{EO} system was computed in \emph{Fed4FIRE}: A constellation of
satellites record images of the Earth in a daily basis. The images are
transferred to a network of ground stations that ingest the data into a cloud computing infrastructure. The data is processed and distributed to end users.

The GEO-Cloud experiment uses in three testbeds: \emph{Virtual Wall},\bonfire and
\emph{PlanetLab}. GEO-Cloud is divided into two sub-experiments:
\begin{itemize}
\item One experiment in a system integrated in \vw and \bonfire.
\item One experiment in \pl.
\end{itemize}

The experiment in \vw and \bonfire emulates the whole \ac{EO} system. The system is constituted by:

\begin{itemize}
\item A \sss including models of satellite constellation and a ground stations
  network.
\item A cloud computing system that implements a novel architecture that
  integrates an \emph{Orchestrator}, a \emph{Processing Chain} component
  based on \ac{EaaS}  with image processors to transform the raw data acquired
  by the satellites in orthorectified images, and finally an \emph{Archive and Catalogue}
  module for storing, cataloging and allocating images.
\end{itemize}

The experiment in \pl consists of the emulation of the networks that constitute
the links between the ground stations to the cloud and from the cloud to the end
users. There, the network features such as bandwidth, loss-rate and latency are monitored and measured. Those parameters once measured are used to update the
network models implemented in \vw.

In the next sections, the detailed design and implementation in testbeds of the GEO-Cloud experiment is fully
described. 

\input{sat-system-design.tex}

\input{spacesystemsimulator.tex}

\input{implementationVW.tex}

\input{cloud-components.tex}

\input{implementationBF.tex}

\input{integrationVWBF.tex}

\input{planetlab.tex}

\input{gui.tex}
