\section{GEO-Cloud Graphical User Interface}

In this section, the \ac{GUI} developed for managing the execution of the defined
scenarios in GEO-Cloud experiment is exposed. First, the architecture is
explained. The components such as \emph{ExperimentController}, \emph{Video
  Component}, \emph{Log Component}, \emph{About Component} and \emph{WorkLoad component} are described. Finally, the workflow is explained.

\subsection{Architecture}

The graphical user interface of GEO-Cloud experiment is composed by the following components:

\begin{itemize}

\item \emph{Experiment Controller}: it manages the \sss turning on or shutting it down.
\item \emph{Video Component}: it shows a video demonstration of the satellite constellation acquiring images at same time that the satellites in \vw.
\item \emph{About Component}: it shows the \emph{About} window where the acknowledments are shown.
\item \emph{Log Component}: it prints the logs which receives from satellites and ground stations.
\item \emph{Workload component}: it plots the workload of the Orchestrator and Processing chain machine.

\end{itemize}

The Figure~\ref{} shows the architecture where the relations between the components are pictured.

%esquema architectur

\subsubsection{Experiment Controller}

This component connects with the \sss for managing it execution. Basically, this component is constituted by the following classes: the ExperimentController class, VWConnection class and JFedParser class. This classes controls, connects and parsers the execution of the \sss, obtains the connections with \sss nodes and process a configuration file in order to obtain the \sss nodes hostnames, respectively.

The ExperimentController sequentially follows the next steps during the execution:
\begin{itemize}
\item First, the JFedParser is created and it parsers the contain of the file namely ``jfed.out'' located 

\end{itemize}

\subsubsection{Video Component}

This 

\subsection{About Component}

\subsection{Log Component}

\subsection{Workload Component}








% Local Variables:
%   coding: utf-8
%   fill-column: 90
%   mode: flyspell
%   ispell-local-dictionary: "american"
%   mode: latex
%   TeX-master: "main"
% End:
