\chapter{Results}
\label{chap:results}

\drop{T}{he} obtained results of the implementation, execution and
validation of the GEO-Cloud experiment are explained. The \emph{PlanetLab}
experiment for measuring the network impairments (bandwidth, loss-rate and
\ac{RTT}) are shown and plotted. These plots represent how the impairments
directly depend on the distance between both source and destination elements.
Then the experiment carried to demonstrate the correct implementation of the
GeoCloud is shown. Then, the evaluation of the architecture using ICE are
described. Finally, the evaluation of the system is explained.

\input{planetlabResults.tex}

\input{geocloudResults.tex}

\section{Publications}

The publications that has led this project are listed as follows:

\begin{itemize}
 
\item Gerardo González, Rubén Pérez, Jonathan Becedas, Manuel
  Latorre and Félix Pedrera, ``Measurement and Modelling of PlanetLab Network
  Impairments for Fed4FIRE’s GEO-Cloud Experiment''. \emph{IEEE 26th
    International Teletraffic Congress - Workshop on Future Internet and
    Distributed Clouds (ITC 2014)}, Karlskrona, Sweden, September 2014.

\item Rubén Pérez, Gerardo González, Jonathan Becedas, Manuel Latorre and
Félix Pedrera, ``TesTest Cloud Computing for Massive Space Data Processing,
Storage and Distribution with Open-Source Geo-Software''. \emph{FOSS4G-Europe Congress - Workshop on Free and Open Source Software
for Geospatial, INSPIRE and Big Data (FOSS4G-Europe 2014)},
Bremen, Germany, July 2014.

\item Jonathan Becedas, Gerardo González, Rubén Pérez, Manuel Latorre and Félix
Pedrera, ``Cloud Architecture for Processing and Distribution of Satellites
Imagery''. \emph{FOSS4G-Europe Congress - Workshop on Free and Open Source Software
for Geospatial, INSPIRE and Big Data (FOSS4G-Europe 2014)},
Bremen, Germany, July 2014.
\item Manuel Latorre, Félix Pedrera Jonathan Becedas, Gerardo González and Rubén
  Pérez, ``Validation of an experimental on-demand cloud infrastructure for Earth
  Observation Web Services''. \emph{FOSS4G-Europe Congress - Workshop on Free and Open
  Source Software for Geospatial, INSPIRE and Big Data (FOSS4G-Europe 2014)},
Bremen, Germany, July 2014.
\item Jonathan Becedas, Gerardo González, Rubén Pérez, Manuel Latorre and Félix
Pedrera, ``Validation of an Experimental Cloud Infrastructure for Earth
Observation Services''. \emph{RAQRS'IV Congress - Workshop on Recent Advances in
Quantitative Remote Sensing}, Valencia, Spain, September 2014.

\end{itemize}
